---
title: "capstone part 2----WiFi matters?"
author: "Li Sun"
date: "November 21, 2015"
output: html_document
---


In this part, I am trying to use small portion of the data whose review contains wifi or internet, that is using the data frame I made "wifidf", to do regression on average stars the business got. By using this model, we are assuming we can separate people's feeling about wifi and all other things by exploring the review text.

#Load nessesary packages and data sets
```{r}
library(dplyr)
library(ggplot2)
library(wordcloud)
#library(RColorBrewer)


wifidf <- readRDS("wifidf.rds")
#fbusi <- readRDS()
stem_wifi_text <- readRDS("stem_wifi_text.rds")
stem_wifi_text[1]

```
# Text mining
```{r}
positive_words <- readLines("http://www.idiap.ch/~apbelis/hlt-course/positive-words.txt")[-c(1:35)]
negtive_words <- readLines("http://r.chrisrooney.co.uk/presentation/data/negative-words.txt")[-c(1:35)]

#Function to count positive words
pos_count <- function(char, pos = c(positive_words, "plus")){
  sum(tolower(strsplit(char, split=" ")[[1]]) %in% pos)
}
#Function to count negative words
neg_count <- function(char, neg = c(negtive_words)){
  sum(tolower(strsplit(char, split=" ")[[1]]) %in% neg)
}

# for(i in 1:nrow(wifidf)){
#   wifidf$npos[i] <- pos_count(wifidf$wifi_sen[i])
#   wifidf$nneg[i] <- neg_count(wifidf$wifi_sen[i])
#   wifidf$ntok[i] <- length(stem_wifi_text[[i]])
# }

for(i in 1:length(stem_wifi_text)){
  wifidf$npos[i] <- pos_count(paste(stem_wifi_text[[i]], collapse = " "))
  wifidf$nneg[i] <- neg_count(paste(stem_wifi_text[[i]], collapse = " "))
  wifidf$ntok[i] <- length(stem_wifi_text[[i]])
}

wifidf$sentw <- (wifidf$npos - wifidf$nneg)/wifidf$ntok
hist(wifidf$sentw, breaks = 100)

#png(file="13.png",width=2500,height=1700,res=350)
ggplot(wifidf, aes(attributes.wifi, sentw))+geom_boxplot(fill="light blue") + labs(x="WIFI status provided by yelp", y="sentiment about wifi")
#qplot(wifidf$sentw ~ wifidf$attributes.wifi, xlab="WIFI status provided by yelp", ylab ="sentiment about wifi")
#dev.off()

# nosent <- filter(wifidf[,-5], sentw==0)
# nosent$wifi_sen[1:10]

# What are people talking about in weird region
filter(wifidf[,-5], sentw < -0.3, attributes.wifi == "free")$wifi_sen
filter(wifidf[,-5], sentw > 0.5, attributes.wifi == "no")$wifi_sen
```


```{r}
#word cloud
mywc <- function(doclist){
  freqdf<-as.data.frame(table(unlist(doclist)),stringsAsFactors=F) 
  wordcloud(freqdf$Var1, freqdf$Freq, max.words=50, colors=brewer.pal(8, "Dark2"))
}

freep <- filter(wifidf[,-5], sentw > 0, attributes.wifi == "free")$wifi_sen
freen <- filter(wifidf[,-5], sentw < 0, attributes.wifi == "free")$wifi_sen
paidp <- filter(wifidf[,-5], sentw > 0, attributes.wifi == "paid")$wifi_sen
paidn <- filter(wifidf[,-5], sentw < 0, attributes.wifi == "paid")$wifi_sen
nop <- filter(wifidf[,-5], sentw > 0, attributes.wifi == "no")$wifi_sen
non <- filter(wifidf[,-5], sentw < 0, attributes.wifi == "no")$wifi_sen



wordcloud(freep, max.words = 50, colors = brewer.pal(8,"Dark2"))
wordcloud(freen, max.words = 50, colors = brewer.pal(8,"Dark2"))
wordcloud(paidp, max.words = 50, colors = brewer.pal(8,"Dark2"))
wordcloud(paidn, max.words = 100, colors = brewer.pal(8,"Dark2"))
wordcloud(nop, max.words = 50, colors = brewer.pal(8,"Dark2"))
wordcloud(non, max.words = 50, colors = brewer.pal(8,"Dark2"))


```


```{r}
df0<-readRDS("yelp_tm.rds")
wifidf2 <- merge(wifidf, df0, by = "review_id")
wifidf2$num

wifidf$pos_num <- wifidf$pos_num - wifidf$npos
wifidf$neg_num <- wifidf$neg_num - wifidf$nneg
wifidf$token_num <- wifidf$token_num - wifidf$ntok
wifidf$sentiment <- (wifidf$pos_num - wifidf$neg_num)/wifidf$token_num

boxplot(wifidf$sentw~wifidf$attributes.wifi)
plot(x=wifidf$sentiment, y=wifidf$stars)
```


#Create new variables for regression on reviews
```{r}
wifidf3 <- wifidf[,c(2:6, 11,12,16:83, 106:114)]
wifidf3<-mutate(wifidf3, token_num = token_num - ntok, pos_num = pos_num - npos, neg_num=neg_num-nneg)
wifidf3 <- mutate(wifidf3, sentiment = (pos_num - neg_num)/token_num)
wifidf3$sentiment[wifidf3$sentiment > 1000 | wifidf3$sentiment < -1000 | is.na(wifidf3$sentiment)] <- rep(0, 36)
sparcity <- sapply(wifidf3, function(x){sum(is.na(x))/length(x)})
wifidf4 <- wifidf3[,sparcity < 0.05]
# maintain only completcases
wifidf4 <- wifidf4[,-4]

#citi
city<-names(sort(table(wifidf4$city), decreasing = T)[1:4])
# we will leave first 5 cities and combine all left as "others"
oricity <- as.character(wifidf4$city)
for(i in 1:nrow(wifidf4)){
  if(oricity[i] %in% city){next}
  else{oricity[i]<-"others"}
}
wifidf4$city <- as.factor(oricity)


#categories
#How many unique categories are there?
uniq_categ <- unique(unlist(wifidf4$categories))
categM <- (uniq_categ %in% wifidf4$categories[[1]]) *1
for(i in 2:nrow(wifidf4)){
  categM <- rbind(categM, (uniq_categ %in% wifidf4$categories[[i]]) *1)
}
colnames(categM) <- uniq_categ
categM <- categM[,-2]
rownames(categM) <- NULL
wifidf4 <- cbind(wifidf4, categM)

```

#Change variable classes
```{r}
sapply(wifidf4, class)
wifidf4$`attributes.Accepts Credit Cards`[sapply(wifidf4$`attributes.Accepts Credit Cards`, length) == 0] <- as.list(rep(999,10))
wifidf4$`attributes.Accepts Credit Cards` <- unlist(wifidf4$`attributes.Accepts Credit Cards`)
wifidf4$`attributes.Accepts Credit Cards`[wifidf4$`attributes.Accepts Credit Cards` > 900] <- NA
wifidf4$attributes.Alcohol <- as.factor(wifidf4$attributes.Alcohol)
wifidf4$`attributes.Noise Level` <- as.factor(wifidf4$`attributes.Noise Level`)
wifidf4$attributes.Attire <- as.factor(wifidf4$attributes.Attire)
wifidf4$attributes.wifi <- as.factor(wifidf4$attributes.wifi)

saveRDS(wifidf4, "wifidf4.rds")

wifidf5 <- wifidf4[, -c(1,2,4,5,40,41)]
#Maintain only complete cases
wifidf5 <- wifidf5[complete.cases(wifidf5),]

```

#Modeling on individual reviews
```{r}
#Remove highly correlated variables
wifidf6 <- wifidf5[,-c(36:41)]
f <- lm(stars~., data=wifidf6)
summary(f)

#Model selection by backwards
fs <- step (f, direction="backward")
summary(fs)
```


#Modeling by weighted regression on only business
```{r}
wifidf7 <- mutate(group_by(wifidf4, business_id), ave_star = mean(stars), ave_sent = mean(sentiment), ave_sentw = mean(sentw), nrev = n())

wifidf7 <- wifidf7[,-c(2,3,4,5,40:49)]
wifidf7 <- wifidf7[complete.cases(wifidf7),]
# unibusi_id<- unique(wifidf7$business_id)
# xdf <- data.frame(business_id=unibusi_id, extra = rep(0, length(unibusi_id)))
# wifidf8 <- merge(xdf, wifidf7[,1:2])
wifidf8 <- wifidf7[!duplicated(wifidf7), ]
wifidf8 <- wifidf8[, -1]

f2 <- lm(ave_star~., data=wifidf8, weights = sqrt(nrev))
summary(f2)
f21 <- lm(ave_star~ave_sent + ave_sentw, data=wifidf8, weights = sqrt(nrev))
summary(f21)
f22 <- step(f21, scope = list(lower=f21, upper=f2), direction="forward", steps=50)
```

